Temporal stability in human interaction networks: sector sizes, topological prominence and time activity

### 2015-10-05 paper.tex
polindo

\section{Conclusions}\label{sec:conc}
The temporal stability reported in this article is very counterintuitive.
These characteristics were expected from current scientific knowledge,
such as the fat tail structure and the preponderance of centrality measures,
but the very small standard deviations of principal components formation (Section~\ref{}),
the presence of the Erd\"os sectors even in networks with
few participants (Section~\ref{}),
and the recurrent activity patterns along different timescales (Section~\ref{}),
goes a step further in characterizing scale-free networks in the context
of the interaction of human individuals.
Maybe secondary, but nonetheless important, the importance of symmetry-related metrics,
which surpassed that of clustering coefficient,
with respect to dispersion of the system in the topological space,
might add to current understanding of how Digraphs differ from
undirected graphs.
Noteworthy is the also very stable fraction participants in each Erd\"os sectors
when the network reaches more than 200 participants (more that 1000 messages).
Benchmarks were derived from email list networks
and the analysis of
networks from Facebook,
Twitter and Participabr might ease hypothesizing
about the generality of such results.
Selected tables and figures sum dozens of pages
and are gathered in
the Supporting Information document.

>>>>

\section{Conclusions}\label{sec:conc}
The temporal stability reported in this article is very counterintuitive.
These characteristics were expected from current scientific knowledge,
such as the fat tail structure and the preponderance of centrality measures,
but the very small standard deviations of principal components formation
(see Sections~\ref{sec:pca} and~\ref{prevalence}),
the presence of the Erd\"os sectors even in networks with
few participants (see Sections~\ref{sectioning} and~\ref{subsec:pih}),
and the recurrent activity patterns along different timescales (see Sections~\ref{sec:mtime} and~\ref{constDisc}),
goes a step further in characterizing scale-free networks in the context
of the interaction of human individuals.
Maybe secondary, but nonetheless important, the importance of symmetry-related metrics,
which surpassed that of clustering coefficient,
with respect to dispersion of the system in the topological space,
might add to current understanding of key-differences between digraphs and
undirected graphs in complex networks.
Noteworthy is the also very stable fraction participants in each Erd\"os sector
when the network reaches more than 200 participants (more that 1000 messages).
Benchmarks were derived from email list networks
and the supplied analysis of
networks from Facebook,
Twitter and Participabr might ease hypothesizing
about the generality of these characteristics.
Selected tables and figures sum dozens of pages
and are gathered in
the Supporting Information document.
